Prediction Assignment Writeup
==========================================================
 
RandomForest libraries used. 
Create correct answers for each of the 20 test data cases of this assignment. 

```{r, echo=FALSE}
options(warn=-1)
suppressWarnings(library(Hmisc))
suppressWarnings(library(caret))
suppressWarnings(library(randomForest))
suppressWarnings(library(foreach))
suppressWarnings(library(doParallel))
set.seed(1024)
```
 
 
```{r, echo=FALSE}
if (!file.exists("pmlTraining.csv")) {
    download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",
                  destfile = "pmlTraining.csv")
}
if (!file.exists("pmlTesting.csv")) {
    download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
                  destfile = "pmlTesting.csv")
}
 
training_data <- read.csv("pmlTraining.csv", na.strings=c("#DIV/0!") )
evaluation_data <- read.csv("pmlTesting.csv", na.strings=c("#DIV/0!") )
```
 
 
```{r, echo=FALSE}
for(i in c(8:ncol(training_data)-1)) {training_data[,i] = as.numeric(as.character(training_data[,i]))}
 
for(i in c(8:ncol(evaluation_data)-1)) {evaluation_data[,i] = as.numeric(as.character(evaluation_data[,i]))}
```
 
Displaying all data in 8 columns as numeric values.
 
```{r}
feature_set <- colnames(training_data[colSums(is.na(training_data)) == 0])[-(1:7)]
model_data <- training_data[feature_set]
feature_set
```
 
Date split into two models, training and testing.
 
```{r}
idx <- createDataPartition(y=model_data$classe, p=0.75, list=FALSE )
training <- model_data[idx,]
testing <- model_data[-idx,]
```
 
Build 5 random forests with 150 trees each.
 
```{r}
registerDoParallel()
x <- training[-ncol(training)]
y <- training$classe
 
rf <- foreach(ntree=rep(150, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
randomForest(x, y, ntree=ntree)
}
```
 
 
Conclusions and Test Data
-------------------------
Model is accurate based in the matrix. Test data around 99% accurate. Test cases almost correct.
 
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
 
 
x <- evaluation_data
x <- x[feature_set[feature_set!='classe']]
answers <- predict(rf, newdata=x)
 
answers
 
pml_write_files(answers)
```
 